MSE and dynamic state variable model with sigma function

### 2018-07-18 doc/MSE_MAR_18.tex
modified slope of prices, reduced sigma and introduced fuel costs

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas and discarding patterns, the model was divided into a 'north' and 'south' area, and twelve fishing seasons per year (Table \ref{t:fishery}). There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns was equal for the two species, and arbitrarily set to 500 per year. The species differed with respect to their nursery grounds: all individuals of species 1 were born in the northern area, while all individuals of species 2 were born in the southern area (Figure \ref{f:distribution}). The maximum age that any individual can reach was 6 years old. During their life, individuals grew in length towards the asymptotic length, which was 50 cm for both species (Figure \ref{f:prices}). Conversion from length to weight was also equal for the two species (Table \ref{t:fishery}). Migration was parameterized so that a gradual diffusion occurred between the two areas, equal to 2.5 percent of the difference in abundance. For the unfished situation this led to a clear segregation of the younger ages over the two areas, while the older ages were equally distributed over the two areas (Figure \ref{f:distribution}). Mortality from natural causes such as predation, diseases, and senescence was assumed to be negligible, and $M_i$ set to 0.0001. Although such absence of natural mortality impossible in reality, one could argue that the model thus mimicked long-lived species.

@@

The model was set up in three consecutive time windows. In the first window of 10 years, newborns entered the population in the absence of fishing. This resulted in a virgin stock status. Then, the fleet of 8000 vessels started fishing in the absence of any fisheries regulations. This window lasted 15 years and gradually resulted in a situation where the stocks were overfished, i.e. the harvest rates were larger than $H_{max}$. During this period the fishery was unmanaged, by meaned with unconstrained quota for both species. Finally, the management procedure started where the HCR, fishing at harvest rates equal to $H_{i,max}$, controls the annual quotas. This last period lasted 15 years.

The two management scenarios considered differ simply by the number of stocks forced to meet the objective of the plan. For this purpose, species 1 was the one to do so in first scenario, while in second scenario both species were controlled by HCR. The comparison among these scenarios allowed the evaluation of costs and benefits, both economic and in terms of risks to both stock and livelihoods, that resulted from the response of individual effort allocation to meet the objective of the management plan.

>>>>

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas, the model was divided into a 'north' and 'south' area, and twelve fishing seasons per year (Table \ref{t:fishery}). There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns was equal for the two species, and arbitrarily set to 500 per year. The species differed with respect to their nursery grounds: all individuals of species 1 were born in the northern area, while all individuals of species 2 were born in the southern area (Figure \ref{f:distribution}). The maximum age that any individual can reach was 6 years old. During their life, individuals grew in length towards the asymptotic length, which was 50 cm for both species (Figure \ref{f:prices}). Conversion from length to weight was also equal for the two species (Table \ref{t:fishery}). Migration was parameterized so that a gradual diffusion occurred between the two areas, equal to 2.5 percent of the difference in abundance. For the unfished situation this led to a clear segregation of the younger ages over the two areas, while the older ages were equally distributed over the two areas (Figure \ref{f:distribution}). Mortality from natural causes such as predation, diseases, and senescence was assumed to be negligible, and $M_i$ set to 0.0001. Although such absence of natural mortality impossible in reality, one could argue that the model thus mimicked long-lived species.

@@

The model was set up in three consecutive time windows. In the first window of 10 years, newborns entered the population in the absence of fishing. This resulted in a virgin stock status. Then, the fleet of 8000 vessels started fishing in the absence of any fisheries regulations. This window lasted 15 years and gradually resulted in a situation where the stocks were overfished, i.e. the harvest rates were larger than $H_{max}$. During this period the fishery was unmanaged, by meaned with unconstrained quota for both species. Finally, to assess the effect of the landing obligation (where discarding is no longer permitted) on the objectives of the MSY, the management procedure started where the HCR, fishing at harvest rates equal to $H_{i,max}$, controls the annual quotas. This last period lasted 15 years.

The two management scenarios considered differ simply by the number of stocks forced to meet the objective of the plan. For this purpose, in a single-stock context: species 1 was the one to do so in first scenario, while in a mixed-fishery context: both species were controlled by HCR in second scenario. The comparison among these scenarios allowed the evaluation of costs and benefits, both economic and in terms of risks to both stock and livelihoods, that resulted from the response of individual effort allocation to meet the objective of the landing obligation regarding the objectives of the CFP, specially the MSY.
